The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-10-17 manuscript/manuscript.tex
Update the offset value

Correlations between the mass of a supermassive black hole (SMBH) and the properties of its host galaxy (e.g., stellar mass \smass, luminosity \lhost) suggest an evolutionary connection. A powerful test of a co-evolution scenario is to measure the relations \mbh-\lhost\ and \mbh-\smass~at high redshift and compare with local estimates. For this purpose, we acquired multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 \hbox{X-ray-selected} broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields. By applying state-of-the-art tools to decompose the \hst\ images, we measured the host galaxy luminosity and stellar mass along with other properties through the 2D model fitting. The black hole mass (\mbh) was determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators. We find the {\it observed} ratio of \mbh/\smass~to {\bf be $2.6\times$ larger at $z\sim1.5$ than in} the local universe, while the scatter is equivalent between the two epochs. \ding{(TB update based on Daeseong's result:) an {\it intrinsic} non-evolving mass ratio is consistent with the data at the 95\% confidence level when accounting for selection effects (estimated using two independent and complementary methods).} The relationship between \mbh\ and host galaxy total luminosity paints a similar picture. Therefore, our results are in agreement, considering the uncertainties, with a scenario where SMBHs and their total host stellar mass and luminosity proceed in lockstep or the growth of the former somewhat predates the latter. Based on an inference of the bulge-to-total mass fraction, the ratio \mbh/\bmass~is significantly offset from the local value {\bf by a factor of $\sim7$ which} persists even after accounting for selection effects. Taken together, these observations are consistent with a scenario in which stellar mass is subsequently transferred from an angular momentum supported component of the galaxy to the pressure supported one through secular processes or minor mergers at a faster rate than mass accretion onto the SMBH.

@@

In Figure~\ref{fig:MM}, we plot the our \mbh -- \smass\ measurements and find that the distributions in this plane for the four samples are similar. However, there is a slight shift of the high-$z$ data towards higher black hole masses at a fixed host mass. In Figure~\ref{fig:MM-vz}, we plot the mass ratio as a function of redshift ({\it right} panel) and the mass ratio difference ($\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{M_*}{10^{10}M_{\odot}})$ which is considered as the difference between the high redshift data and the best-fit local relation; {\it left} panel). For our high-$z$ sample, we find the averaged $\Delta \log \mathcal M_{\rm BH}$ to be $0.32$, a factor of two higher than the local mass ratio as indicated by the top blue circle in Figure~\ref{fig:MM-vz}.

@@

We find the average ``observed" ratio between the mass of a SMBH and either their total host luminosity or total stellar mass is larger at $z\sim1.5$, {\bf by $0.41$~dex (a factor of $\sim2.7$) and  $0.43$~dex (a factor of $\sim2.6$), respectively}, as compared to that in the local universe. 
{\bf However, taking into account uncertainties and the bias due to selection effect could bias, the offset to the local universe is only marginally significant.} 
%these correlations are consistent with those in the local universe within the 95\% confidence limits. }
Even with the remaining uncertainties in the corrections for selection, we are confident that any evolution in the \mbh/\smass\ relation is at the most a factor of two with the case of no evolution entirely plausible.

>>>>

Correlations between the mass of a supermassive black hole (SMBH) and the properties of its host galaxy (e.g., stellar mass \smass, luminosity \lhost) suggest an evolutionary connection. A powerful test of a co-evolution scenario is to measure the relations \mbh-\lhost\ and \mbh-\smass~at high redshift and compare with local estimates. For this purpose, we acquired multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 \hbox{X-ray-selected} broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields. By applying state-of-the-art tools to decompose the \hst\ images, we measured the host galaxy luminosity and stellar mass along with other properties through the 2D model fitting. The black hole mass (\mbh) was determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators. We find the {\it observed} ratio of \mbh/\smass~to {\bf be $2.7\times$ larger at $z\sim1.5$ than in} the local universe, while the scatter is equivalent between the two epochs. \ding{(TB update based on Daeseong's result:) an {\it intrinsic} non-evolving mass ratio is consistent with the data at the 95\% confidence level when accounting for selection effects (estimated using two independent and complementary methods).} The relationship between \mbh\ and host galaxy total luminosity paints a similar picture. Therefore, our results are in agreement, considering the uncertainties, with a scenario where SMBHs and their total host stellar mass and luminosity proceed in lockstep or the growth of the former somewhat predates the latter. Based on an inference of the bulge-to-total mass fraction, the ratio \mbh/\bmass~is significantly offset from the local value {\bf by a factor of $\sim7$ which} persists even after accounting for selection effects. Taken together, these observations are consistent with a scenario in which stellar mass is subsequently transferred from an angular momentum supported component of the galaxy to the pressure supported one through secular processes or minor mergers at a faster rate than mass accretion onto the SMBH.

@@

In Figure~\ref{fig:MM}, we plot the our \mbh -- \smass\ measurements and find that the distributions in this plane for the four samples are similar. However, there is a slight shift of the high-$z$ data towards higher black hole masses at a fixed host mass. In Figure~\ref{fig:MM-vz}, we plot the mass ratio as a function of redshift ({\it right} panel) and the mass ratio difference ($\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{M_*}{10^{10}M_{\odot}})$ which is considered as the difference between the high redshift data and the best-fit local relation; {\it left} panel). For our high-$z$ sample, we find the averaged $\Delta \log \mathcal M_{\rm BH}$ to {\bf be $0.43\pm0.06$, a factor of $~\sim2.7$ higher} than the local mass ratio as indicated by the top blue circle in Figure~\ref{fig:MM-vz}.

@@

We find the average ``observed" ratio between the mass of a SMBH and either their total host luminosity or total stellar mass is larger at $z\sim1.5$, {\bf by $0.41$~dex (a factor of $\sim2.6$) and  $0.43$~dex (a factor of $\sim2.7$), respectively}, as compared to that in the local universe. 
{\bf However, taking into account uncertainties and the bias due to selection effect could bias, the offset to the local universe is only marginally significant.} 
%these correlations are consistent with those in the local universe within the 95\% confidence limits. }
Even with the remaining uncertainties in the corrections for selection, we are confident that any evolution in the \mbh/\smass\ relation is at the most a factor of two with the case of no evolution entirely plausible.
